\documentclass[oneside]{article}

\usepackage[left=1cm,right=1cm,twosideshift=0cm, top=1cm,bottom=1cm]{geometry}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage[french]{babel}
\usepackage{garamond}
%\usepackage{aeguill}

\begin{document}
\pagestyle{empty}
\center\sffamily\fontseries{sbc}\selectfont\Large\color{black!60!cyan}

{\huge\garamond\normalfont\color{black} People are illogical, unreasonable, and self-centered.}\\
Love them anyway.

\vfill

{\huge\garamond\normalfont\color{black} If you do good, people will accuse you of selfish ulterior
motives.}\\
Do good anyway.

\vfill

{\huge\garamond\normalfont\color{black} If you are successful, you will win false friends and true
enemies.}\\
Succeed anyway.

\vfill

{\huge\garamond\normalfont\color{black} The good you do today will be forgotten tomorrow.}\\
Do good anyway.

\vfill

{\huge\garamond\normalfont\color{black} Honesty and frankness make you vulnerable.}\\
Be honest and frank anyway.

\vfill

{\huge\garamond\normalfont\color{black} The biggest men and women with the biggest ideas can be shot down by the
smallest men and women with the smallest minds.}\\
Think big anyway.

\vfill

{\huge\garamond\normalfont\color{black} People favor underdogs but follow only top dogs.}\\
Fight for a few underdogs anyway.

\vfill

{\huge\garamond\normalfont\color{black} What you spend years building may be destroyed overnight.}\\
Build anyway.

\vfill

{\huge\garamond\normalfont\color{black} People really need help but may attack you if you do help them.}\\
Help people anyway.

\vfill

{\huge\garamond\normalfont\color{black} Give the world the best you have and you'll get kicked in the
teeth.}\\
Give the world the best you have anyway.

\vfill
\raggedright

\garamond\normalfont\color{black} The Paradoxical Commandments\\
by Dr. Kent M. Keith

\end{document}
